---
title: "Module 15 Challenge"
author: "Madelyn Mathai"
date: "3/27/2021"
output: html_document
---
## Libraries
```{r setup, include=FALSE}
library(tidyverse)
library(ggplot2)
library(jsonlite)
library(dplyr)
```



## Set Working Directory
```{r cars} 
setwd("~/Desktop/Data-Analytics/Modules/15_Module/MechaCar_Statistical_Analysis")
```


## Deliverable 1

### The MechaCar_mpg.csv file is imported and read into a dataframe (5 pt)
```{r}
mecha_car <- read.csv("MechaCar_mpg.csv")
```




### An RScript is written for a linear regression model to be performed on all six variables (10 pt)
```{r pressure, echo=FALSE}
lm(mpg ~ vehicle_length + vehicle_weight + ground_clearance + spoiler_angle + AWD, mecha_car)

```
### An RScript is written to create the statistical summary of the linear regression model with the intended p-values (10 pt)
```{r}
summary(lm(mpg ~ vehicle_length + vehicle_weight + ground_clearance + spoiler_angle + AWD, mecha_car))
```


## Deliverable 2

### The Suspension_Coil.csv file is imported and read into a dataframe (5 pt)
```{r}
suspension_coil <- read.csv("Suspension_Coil.csv")
```
### An RScript is written to create a total summary dataframe that has the mean, median, variance, and standard deviation of the PSI for all manufacturing lots (10 pt)
```{r}


summary_table <- suspension_coil %>% 
  summarize(Mean = mean(PSI),Median = median(PSI),Variance = var(PSI), SD = sd(PSI))

```
### An RScript is written to create a lot summary dataframe that has the mean, median, variance, and standard deviation for each manufacturing lot (10 pt)
```{r}
lot_summary <- suspension_coil %>% group_by(Manufacturing_Lot) %>% summarize(Mean = mean(PSI),Median = median(PSI),Variance = var(PSI), SD = sd(PSI), .groups = 'keep')
```

## Deliverable 3

## An RScript is written for t-test that compares all manufacturing lots against mean PSI of the population (5 pt)

```{r}
t.test(suspension_coil$PSI, mu=1500)
```

## An RScript is written for three t-tests that compare each manufacturing lot against mean PSI of the population (10 pt)

```{r}

t.test(subset(suspension_coil,Manufacturing_Lot=="Lot1")$PSI, mu = 1500)
t.test(subset(suspension_coil,Manufacturing_Lot=="Lot2")$PSI, mu = 1500)
t.test(subset(suspension_coil,Manufacturing_Lot=="Lot3")$PSI, mu = 1500)
```

